Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-21 documents/BrazilSlides/slides.tex
More progress, added noise plots normalized

\begin{frame}
    \frametitle{Parameterizing PVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
        \item Use unitary transformation again
        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
        \item PVMs are computationally more efficient
    \end{itemize}
    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
\end{frame}

\begin{frame}
    \frametitle{Uniform Noise}
    \[ \s{U}_{\varepsilon}\br{P} = \br{1 + \varepsilon} P + \varepsilon \s{U} \]
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
    \end{center}
    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    % \begin{center}
    %     \begin{tikzpicture}
    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
    %         \draw[] (1*\ts,0) node[]{$=$};
    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
    %         \draw[] (3*\ts,0) node[]{$+$};
    %         \draw[] (4*\ts,0) node[]{$\delta$};
    %     \end{tikzpicture}
    % \end{center}
\end{frame}
\begin{frame}
    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
\end{frame}

\begin{frame}
    \frametitle{Maximally Violating Distributions}
    \begin{itemize}
        \item Able to out-perform violation provided by Fritz distribution
        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
        \item Violation very sensitive to the initial parameters $\la_{(0)}$
        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{itemize}
        \item New causal compatibility inequalities have been found for the TS
        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
        \item Proof of non-classicality is robust to noise
        \item Fritz witness-able by party symmetric inequalities
        \item Maximally violating distributions are different than Fritz but also similar
        \item Further research is necessary
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
    \end{gather*}
    \begin{itemize}
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{01}\bra{01}, \ket{11}\bra{11}, \ket{00}\bra{00}, \ket{10}\bra{10}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
    \end{itemize}
\end{frame}

>>>>

\begin{frame}
    \frametitle{Parameterizing PVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
        \item Use unitary transformation again
        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
        \item PVMs are computationally more efficient
    \end{itemize}
    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
\end{frame}
\begin{frame}
    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
\end{frame}

\begin{frame}
    \frametitle{Maximally Violating Distributions}
    \begin{itemize}
        \item Able to out-perform violation provided by Fritz distribution
        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
        % \item Violation very sensitive to the initial parameters $\la_{(0)}$
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Uniform Noise}
    \[ \s{U}_{\varepsilon}\br{P} = \br{1 - \varepsilon} P + \varepsilon \s{U} \]
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
    \end{center}
    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    % \begin{center}
    %     \begin{tikzpicture}
    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
    %         \draw[] (1*\ts,0) node[]{$=$};
    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
    %         \draw[] (3*\ts,0) node[]{$+$};
    %         \draw[] (4*\ts,0) node[]{$\delta$};
    %     \end{tikzpicture}
    % \end{center}
\end{frame}

\begin{frame}
    \frametitle{Robust to Noise}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/noise/four_rep_inequalities_uniform_noise.pdf}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Robust to Noise Zoomed}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/noise/four_rep_inequalities_uniform_noise_zoomed.pdf}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Noisy Non-locality}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
    \end{center}
    \[ \probplotvalue{255, 255, 255} = 0.00133 \]
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
    \begin{enumerate}
        \item Inflation technique capable of producing polynomial inequalities with quantum/classical witnesses
        \item Fritz witness-able by party-symmetric inequalities
        \item Maximally violating distributions require non-maximally entangled states
    \end{enumerate}
\end{frame}

@@
